---
title: "| Business Analytics  \n| Bonus point sheet - Answers\n"
author: 'Venkata Subramani Renduchintala / matriculation number: 16-905-416'
date: "15.06.2018"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
library("graphics")
library("ggplot2")
library("stringi")
library("reshape2")
library("caret")
library("utils")
library("datasets")
library("class")
library("rpart")
library("party")
```

```{r Load Survey.csv}
surveyCsvPath <- './survey.csv'
#print(surveyCsvPath)
s.studentAnswers <- read.csv(surveyCsvPath, header = TRUE, sep = ",")


dim(s.studentAnswers)
str(s.studentAnswers)
```


## Exercise 1

### a) Solution:
###Use the package ggplot2 to create a point plot comparing the age and pulse of the participants. 
###Color each point according to the gender of the person and additionally label the axis appropriately. 
###Furthermore, change the color of the points such that males are highlighted with a dark blue color and females in dark red.
```{r Point Plot comparing age and pulse of participants}
#create the sample data frame with age and pulse of the participants
df <- reshape2::melt(s.studentAnswers, id.vars=c("Age", "Sex", "Pulse"))
#omit NA values
df <- na.omit(df)
```

```{r Ex 1a Plot}
#Plot
Ex1aPlot <- ggplot2::ggplot(df, aes(x=Age, y=Pulse)) + 
  geom_point(aes(color = Sex)) + 
  scale_color_manual(values=c("darkred", "darkblue"))
print(Ex1aPlot)
```



### b) Solution:
####Use ggplot2 to create boxplot comparing the age distribution of males and females.
####Cut the y-axis at a maximum age of 30 for better readability. Interpret your results
```{r Box Plot}
dfb <- melt(s.studentAnswers, id.vars=c("Age", "Sex"))
dfb <- na.omit(dfb);

```

```{r Ex 1b Plot}
ageDistributionPlot <- ggplot(dfb, aes(x=Sex, y=Age)) + 
  geom_boxplot() + 
  labs(x="Gender", y="Age") +
  ylim(10,30)

print(ageDistributionPlot)

#Interpretation of Result
dfb.female <- dfb[which(dfb$Sex=='Female'), ]
median(dfb.female$Age)
#18.417
dfb.male <- dfb[which(dfb$Sex=='Male'), ]
median(dfb.male$Age)
#18.917
```

## Exercise 2
```{r Exercise 2 Setup}
#data load
data("mtcars")
head(mtcars)
dim(mtcars)
summary(mtcars)
```


```{r Ex 2a Linear Regression - Model estimation}
#dependent_variable: miles per gallon mpg
#INdependent variable: weight wt

#linear regression
fit <- lm(mpg ~ wt, data = mtcars)
summary(fit)
```
#Interpret the results with regard to our initial question [How is the weight of a car affecting its consumption?]
# The impact of weight negatively impact the miles per gallon (-5.3445)
# Model estimated: mpg = 37.2851 - 5.3445 (wt)
#This model has good fit at R2 of 0.7528

##Visualize the trendline between the two variables, i. e. wt and mpg. In addition, add the observations to the plot and add labels to the axis
```{r Ex 2a ggplot of the estimated model}
fit_visual <- ggplot(data = mtcars, aes(y=mpg, x=wt)) +
  geom_point(aes(size=hp, color=as.factor(cyl))) + 
  geom_smooth(method = "lm") +
  labs(y = "Miles per gallon", x= "Weight of car") +
  scale_color_discrete(name=("cyl"))

print(fit_visual)
```

##Now estimate a new model (called M in the following) which additionally contains the number of cylinders cyl and the number of forward gears gear: mpg = β0 + β1 wt + β2 cyl + β3 gear
```{r Ex 2b Estimation of model M}
M <- lm(formula = mpg ~ wt + cyl + gear, data = mtcars)
summary(M)
```
# the coffecients are β0 = 42.3864, β1 = -3.3921, β2 = -1.5280, β3 = -0.5229
# wt('***') has the highest significance on the mpg of the car. Next the cyl('**') of the car is next interms of its significance. gear has the least significance on the model
#This model has very good fit at R2 of 0.8329

## Exercise 2c Split the data into training and test set. Use 30% of the data for training and 70% of the data for testing. Reestimate the model m by only using training data. Predict the mpg variable for the test data. What is the root mean squared error?

```{r Ex 2c Split of data set}
data("mtcars")
#always constant
set.seed(50)

inTrain <- createDataPartition(mtcars$mpg, p = 0.3, list = FALSE )

training_set <- mtcars[inTrain, ]
test_set <- mtcars[-inTrain, ]

```

```{r Ex 2c Re-estimation of model M using training data }
fit_training_set <- lm(formula = mpg ~ ., data = training_set)

summary(fit_training_set)
```

```{r Ex 2c Prediction of mpg and RMSE}
prediction_mpg <- predict(fit_training_set, test_set)

rmse <- sqrt(mean((prediction_mpg - test_set$mpg)^2))
rmse

#Validation
RMSE(prediction_mpg, test_set$mpg)
```


