---
title: |
  | Business Analytics  
  | Bonus point sheet - Answers
author: 'Venkata Subramani Renduchintala / matriculation number: 16-905-416'
date: "27.05.2018"
output:
  pdf_document: default
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE)
library(graphics)
#library(grid)
#library(markdown)
#library(logging)
library(ggplot2)
library(reshape2)
#library(csvread)
#library(tidyverse)
#library(class)
#library(caret)
#library(csv)
#library(csvread)
#library(data.table)
#library(datasets)
#library(formatR)
#library(Matrix)
#library(utils)
#library(gridExtra)
```

```{r Load Survey.csv}
surveyCsvPath <- './survey.csv'
#print(surveyCsvPath)
s.studentAnswers <- read.csv(surveyCsvPath, header = TRUE, sep = ",")
summary(s.studentAnswers)
s.studentAnswers$id <- row.names(s.studentAnswers)
dim(s.studentAnswers)
#print(s.studentAnswers)
```


## Exercise 1

### a) Solution:
###Use the package ggplot2 to create a point plot comparing the age and pulse of the participants. 
###Color each point according to the gender of the person and additionally label the axis appropriately. 
###Furthermore, change the color of the points such that males are highlighted with a dark blue color and females in dark red.
```{r Point Plot comparing age and pulse of participants}
#create the sample data frame with age and pulse of the participants
df <- melt(s.studentAnswers, id.vars=c("Age", "Sex", "Pulse"))
#omit NA values
df <- na.omit(df)

df
```

```{r Ex 1a Plot}
#Plot
Ex1aPlot <- ggplot2::ggplot(df, aes(x=Age, y=Pulse)) + 
  geom_point(aes(color = Sex)) + 
  scale_color_manual(values=c("darkred", "darkblue"))
print(Ex1aPlot)
```



### b) Solution:
####Use ggplot2 to create boxplot comparing the age distribution of males and females.
####Cut the y-axis at a maximum age of 30 for better readability. Interpret your results
```{r Box Plot}
dfb <- melt(s.studentAnswers, id.vars=c("Age", "Sex"))
dfb <- na.omit(dfb);
dfb

```

```{r Ex 1b Plot}
ageDistributionPlot <- ggplot(dfb, aes(x=Sex, y=Age)) + 
  geom_boxplot() + 
  labs(x="Gender", y="Age") +
  ylim(10,30)

print(ageDistributionPlot)

#Interpretation of Result
dfb.female <- dfb[which(dfb$Sex=='Female'), ]
median(dfb.female$Age)
#18.417
dfb.male <- dfb[which(dfb$Sex=='Male'), ]
median(dfb.male$Age)
#18.917
```

## Exercise 2
```{r Exercise 2 Setup}
#data load
d_mtcars <- data("mtcars")
```


```{r Ex 2a}

```

